Trends of SDR in Thessaloniki

### 2023-06-25 DHI_GHI_3_trends_consistency.tex
Commit 2023-06-26 01:17

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1410}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1795}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1795}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1923}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1923}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1154}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\centering
~
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
PositiveSum
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
NegativeSum
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
PositiveMean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
NegativeMean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Sum
\end{minipage} \\
\midrule
\endhead
\textbf{1993} & 2232 & -3205 & 16.06 & -31.43 & -973.5 \\
\textbf{1994} & 4452 & -5575 & 22.83 & -35.29 & -1123 \\
\textbf{1995} & 3407 & -5415 & 21.29 & -30.6 & -2009 \\
\textbf{1996} & 2788 & -7750 & 16.79 & -41.44 & -4962 \\
\textbf{1997} & 4470 & -6190 & 22.81 & -39.17 & -1719 \\
\textbf{1998} & 4367 & -6098 & 22.06 & -40.12 & -1731 \\
\textbf{1999} & 4700 & -5052 & 22.49 & -33.02 & -352.4 \\
\textbf{2000} & 5692 & -3631 & 23.23 & -32.71 & 2061 \\
\textbf{2001} & 4570 & -5386 & 23.08 & -36.89 & -816 \\
\textbf{2002} & 4535 & -5942 & 23.62 & -36.01 & -1407 \\
\textbf{2003} & 4989 & -5994 & 24.46 & -38.67 & -1004 \\
\textbf{2004} & 4499 & -5379 & 21.63 & -36.35 & -880 \\
\textbf{2005} & 4613 & -3980 & 23.66 & -29.26 & 633.2 \\
\textbf{2006} & 4764 & -4385 & 23.58 & -32.97 & 378.7 \\
\textbf{2007} & 4446 & -4126 & 21.9 & -36.19 & 319.5 \\
\textbf{2008} & 5096 & -4847 & 22.06 & -38.16 & 249 \\
\textbf{2009} & 5253 & -5057 & 26.27 & -35.61 & 196.8 \\
\textbf{2010} & 3749 & -4362 & 23.14 & -36.35 & -613.4 \\
\textbf{2011} & 4780 & -4629 & 22.44 & -38.26 & 150.5 \\
\textbf{2012} & 4944 & -4277 & 21.5 & -40.35 & 667.3 \\
\textbf{2013} & 5326 & -4362 & 23.88 & -34.08 & 964.2 \\
\textbf{2014} & 4270 & -5710 & 21.57 & -38.07 & -1440 \\
\textbf{2015} & 5612 & -4511 & 27.11 & -36.09 & 1101 \\
\textbf{2016} & 6263 & -4623 & 27.23 & -35.03 & 1640 \\
\textbf{2017} & 6655 & -4315 & 26.94 & -37.85 & 2340 \\
\textbf{2018} & 5163 & -5085 & 24.59 & -34.83 & 78.02 \\
\textbf{2019} & 5472 & -3791 & 23.39 & -32.97 & 1681 \\
\textbf{2020} & 5989 & -3791 & 25.49 & -33.84 & 2199 \\
\textbf{2021} & 5750 & -4535 & 24.47 & -35.16 & 1215 \\
\textbf{2022} & 6231 & -4079 & 25.33 & -35.47 & 2151 \\
\textbf{2023} & 2958 & -1952 & 32.51 & -34.85 & 1006 \\
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1410}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1795}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1795}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1923}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1923}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1154}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\centering
~
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
PositiveSum
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
NegativeSum
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
PositiveMean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
NegativeMean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Sum
\end{minipage} \\
\midrule
\endhead
\textbf{1993} & 2814 & -3584 & 21.48 & -33.19 & -770.5 \\
\textbf{1994} & 5696 & -5936 & 28.77 & -38.8 & -240 \\
\textbf{1995} & 4001 & -6110 & 27.98 & -31.66 & -2109 \\
\textbf{1996} & 3804 & -8259 & 25.36 & -40.69 & -4456 \\
\textbf{1997} & 4762 & -6823 & 27.06 & -38.33 & -2060 \\
\textbf{1998} & 4678 & -6597 & 25.85 & -39.04 & -1919 \\
\textbf{1999} & 5594 & -5572 & 28.11 & -34.19 & 21.55 \\
\textbf{2000} & 5954 & -4077 & 26.35 & -31.36 & 1877 \\
\textbf{2001} & 4426 & -5877 & 24.73 & -36.5 & -1451 \\
\textbf{2002} & 5201 & -6534 & 30.06 & -35.9 & -1333 \\
\textbf{2003} & 5346 & -6573 & 27.84 & -39.36 & -1228 \\
\textbf{2004} & 4671 & -5968 & 26.54 & -33.16 & -1297 \\
\textbf{2005} & 5624 & -4485 & 30.9 & -30.31 & 1139 \\
\textbf{2006} & 5677 & -4802 & 30.36 & -32.67 & 875 \\
\textbf{2007} & 5241 & -4427 & 27.3 & -35.42 & 813.7 \\
\textbf{2008} & 5997 & -5223 & 28.29 & -36.02 & 773.4 \\
\textbf{2009} & 5527 & -5536 & 29.87 & -35.26 & -9.141 \\
\textbf{2010} & 3575 & -4751 & 24.66 & -34.68 & -1176 \\
\textbf{2011} & 4797 & -5050 & 24.98 & -35.81 & -253.1 \\
\textbf{2012} & 5341 & -4680 & 25.8 & -36.57 & 660.7 \\
\textbf{2013} & 5225 & -4814 & 25.49 & -32.97 & 410.7 \\
\textbf{2014} & 4806 & -6218 & 25.98 & -38.15 & -1412 \\
\textbf{2015} & 5698 & -4929 & 29.22 & -35.98 & 768.7 \\
\textbf{2016} & 6797 & -5042 & 30.75 & -36.01 & 1755 \\
\textbf{2017} & 6495 & -4752 & 29.12 & -34.44 & 1743 \\
\textbf{2018} & 5927 & -5644 & 31.03 & -34.21 & 283.1 \\
\textbf{2019} & 5870 & -4292 & 28.08 & -30.88 & 1578 \\
\textbf{2020} & 6083 & -4301 & 28.83 & -31.63 & 1781 \\
\textbf{2021} & 6692 & -4976 & 29.88 & -35.54 & 1716 \\
\textbf{2022} & 6803 & -4447 & 28.83 & -35.57 & 2356 \\
\textbf{2023} & 3233 & -2072 & 36.33 & -35.72 & 1161 \\
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1410}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1795}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1795}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1923}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1923}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1154}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\centering
~
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
PositiveSum
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
NegativeSum
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
PositiveMean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
NegativeMean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Sum
\end{minipage} \\
\midrule
\endhead
\textbf{1993} & 555.1 & -1190 & 20.56 & -27.05 & -635.2 \\
\textbf{1994} & 661.9 & -1754 & 18.39 & -24.7 & -1092 \\
\textbf{1995} & 640.4 & -1042 & 18.3 & -21.7 & -401.2 \\
\textbf{1996} & 873 & -1718 & 26.46 & -28.17 & -845.2 \\
\textbf{1997} & 1272 & -1106 & 23.56 & -26.98 & 166.2 \\
\textbf{1998} & 1049 & -992.1 & 20.58 & -20.67 & 57.34 \\
\textbf{1999} & 714.5 & -1368 & 17.43 & -20.73 & -653.8 \\
\textbf{2000} & 972.2 & -1160 & 23.15 & -22.74 & -187.7 \\
\textbf{2001} & 1005 & -655.4 & 24.5 & -18.73 & 349.2 \\
\textbf{2002} & 1166 & -1155 & 21.2 & -23.56 & 11.55 \\
\textbf{2003} & 1045 & -1142 & 24.31 & -22.83 & -96.28 \\
\textbf{2004} & 1356 & -646.1 & 27.68 & -19.58 & 710.1 \\
\textbf{2005} & 825.7 & -1101 & 20.14 & -20.78 & -275.8 \\
\textbf{2006} & 941.4 & -1006 & 21.89 & -21.86 & -64.25 \\
\textbf{2007} & 654.3 & -1183 & 21.81 & -25.71 & -528.3 \\
\textbf{2008} & 845 & -1394 & 22.84 & -21.78 & -549 \\
\textbf{2009} & 839.7 & -755.1 & 22.69 & -22.21 & 84.59 \\
\textbf{2010} & 792.5 & -529.7 & 23.31 & -21.19 & 262.8 \\
\textbf{2011} & 1305 & -775.3 & 26.1 & -23.49 & 529.9 \\
\textbf{2012} & 1132 & -1052 & 25.15 & -25.05 & 79.83 \\
\textbf{2013} & 1382 & -776.3 & 27.1 & -18.05 & 605.7 \\
\textbf{2014} & 856.1 & -815.9 & 23.14 & -19.9 & 40.2 \\
\textbf{2015} & 949 & -515.4 & 21.09 & -20.61 & 433.7 \\
\textbf{2016} & 1287 & -1040 & 24.76 & -22.12 & 247.8 \\
\textbf{2017} & 971.9 & -737.2 & 22.6 & -21.06 & 234.7 \\
\textbf{2018} & 1244 & -867.5 & 24.4 & -23.44 & 376.8 \\
\textbf{2019} & 928.5 & -866.3 & 23.81 & -21.13 & 62.18 \\
\textbf{2020} & 1196 & -579.6 & 22.15 & -17.56 & 616.7 \\
\textbf{2021} & 1048 & -844.3 & 16.64 & -16.56 & 203.8 \\
\textbf{2022} & 1112 & -784.9 & 21.8 & -19.14 & 326.9 \\
\textbf{2023} & 131.9 & -203 & 10.99 & -20.3 & -71.12 \\
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1410}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1795}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1795}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1923}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1923}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1154}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\centering
~
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
PositiveSum
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
NegativeSum
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
PositiveMean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
NegativeMean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Sum
\end{minipage} \\
\midrule
\endhead
\textbf{1993} & 19.08 & -48.52 & 6.36 & -9.704 & -29.44 \\
\textbf{1994} & 26.02 & -74.45 & 5.204 & -10.64 & -48.42 \\
\textbf{1995} & 26.9 & -93 & 5.38 & -15.5 & -66.1 \\
\textbf{1996} & 3.185 & -182.2 & 1.592 & -18.22 & -179 \\
\textbf{1997} & 26.52 & -81.3 & 8.84 & -9.033 & -54.78 \\
\textbf{1998} & 27.93 & -76.09 & 5.586 & -10.87 & -48.16 \\
\textbf{1999} & 7.774 & -24.16 & 1.943 & -3.02 & -16.39 \\
\textbf{2000} & 77.82 & -18.31 & 8.646 & -6.102 & 59.51 \\
\textbf{2001} & 49.51 & -76.54 & 9.901 & -10.93 & -27.03 \\
\textbf{2002} & 38.91 & -84.7 & 12.97 & -9.411 & -45.78 \\
\textbf{2003} & 29.84 & -56.12 & 4.974 & -9.354 & -26.28 \\
\textbf{2004} & 28.81 & -57.29 & 4.802 & -9.548 & -28.48 \\
\textbf{2005} & 33.86 & -14.68 & 4.837 & -3.669 & 19.19 \\
\textbf{2006} & 37.15 & -35.07 & 7.43 & -5.844 & 2.085 \\
\textbf{2007} & 24.02 & -15.11 & 4.805 & -3.022 & 8.915 \\
\textbf{2008} & 50.75 & -31.9 & 7.25 & -6.38 & 18.85 \\
\textbf{2009} & 56.6 & -55.74 & 8.086 & -11.15 & 0.8636 \\
\textbf{2010} & 24.77 & -38.35 & 6.191 & -9.587 & -13.58 \\
\textbf{2011} & 24.73 & -28.67 & 4.122 & -5.733 & -3.935 \\
\textbf{2012} & 45 & -23.46 & 5.624 & -7.819 & 21.54 \\
\textbf{2013} & 64.93 & -36.73 & 8.116 & -9.184 & 28.2 \\
\textbf{2014} & 20.71 & -64.85 & 4.141 & -9.264 & -44.14 \\
\textbf{2015} & 92.01 & -45.21 & 13.14 & -11.3 & 46.8 \\
\textbf{2016} & 73.43 & -18.02 & 8.159 & -6.007 & 55.41 \\
\textbf{2017} & 89.19 & -11.66 & 9.91 & -3.886 & 77.53 \\
\textbf{2018} & 51.06 & -44.16 & 7.294 & -8.832 & 6.901 \\
\textbf{2019} & 61.82 & -17.06 & 8.831 & -3.413 & 44.75 \\
\textbf{2020} & 97.56 & -20.95 & 10.84 & -6.983 & 76.61 \\
\textbf{2021} & 60.92 & -21.37 & 8.703 & -4.274 & 39.55 \\
\textbf{2022} & 94.15 & -18.65 & 11.77 & -4.662 & 75.5 \\
\textbf{2023} & 55.86 & -21.35 & 13.96 & -21.35 & 34.51 \\
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1410}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1795}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1795}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1923}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1923}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1154}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\centering
~
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
PositiveSum
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
NegativeSum
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
PositiveMean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
NegativeMean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Sum
\end{minipage} \\
\midrule
\endhead
\textbf{1996} & 1.041 & -32.43 & 1.041 & -16.21 & -31.39 \\
\textbf{1997} & 30.94 & -13.28 & 15.47 & -6.639 & 17.66 \\
\textbf{1998} & 22.21 & -11.6 & 7.405 & -5.802 & 10.61 \\
\textbf{2000} & 5.152 & -11.35 & 5.152 & -11.35 & -6.197 \\
\textbf{2001} & 17.63 & -11.37 & 17.63 & -11.37 & 6.265 \\
\textbf{2002} & 35.68 & -15.07 & 17.84 & -7.534 & 20.61 \\
\textbf{2003} & 31.3 & -26.37 & 15.65 & -13.19 & 4.926 \\
\textbf{2005} & 0.5237 & -13.4 & 0.5237 & -4.466 & -12.87 \\
\textbf{2006} & 20.63 & -22.47 & 6.878 & -11.24 & -1.839 \\
\textbf{2008} & 1.037 & -22.67 & 0.5185 & -7.558 & -21.64 \\
\textbf{2011} & 9.071 & -7.749 & 4.535 & -7.749 & 1.322 \\
\textbf{2012} & 18.89 & -26.75 & 9.443 & -26.75 & -7.868 \\
\textbf{2013} & 23.84 & -3.169 & 11.92 & -3.169 & 20.67 \\
\textbf{2016} & 15.27 & -12.07 & 7.633 & -4.024 & 3.193 \\
\textbf{2021} & 15.2 & -16.53 & 5.068 & -8.266 & -1.329 \\
\bottomrule
\end{longtable}

@@

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_3_trends_consistency_files/figure-latex/CumulativeSZASumDir-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_3_trends_consistency_files/figure-latex/CumulativeSZASumDir-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_3_trends_consistency_files/figure-latex/CumulativeSZASumDir-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_3_trends_consistency_files/figure-latex/CumulativeSZASumDir-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_3_trends_consistency_files/figure-latex/CumulativeSZASumDir-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{DHI_GHI_3_trends_consistency_files/figure-latex/CumulativeSZASumDir-6} \end{center}

>>>>

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1410}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1795}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1795}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1923}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1923}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1154}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\centering
~
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
PositiveSum
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
NegativeSum
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
PositiveMean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
NegativeMean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Sum
\end{minipage} \\
\midrule
\endhead
\textbf{1993} & 2610 & -3026 & 18 & -31.52 & -415.8 \\
\textbf{1994} & 5058 & -5349 & 24.79 & -35.9 & -291.5 \\
\textbf{1995} & 3670 & -5098 & 22.38 & -29.47 & -1429 \\
\textbf{1996} & 3269 & -7514 & 19.23 & -41.06 & -4245 \\
\textbf{1997} & 5002 & -5946 & 24.88 & -38.87 & -944.7 \\
\textbf{1998} & 4977 & -5880 & 23.59 & -42.3 & -902.3 \\
\textbf{1999} & 5124 & -4687 & 23.94 & -31.67 & 437.1 \\
\textbf{2000} & 6492 & -3419 & 25.97 & -32.25 & 3073 \\
\textbf{2001} & 4913 & -5082 & 23.97 & -36.56 & -168.3 \\
\textbf{2002} & 5152 & -5694 & 26.56 & -34.93 & -542.2 \\
\textbf{2003} & 5420 & -5678 & 25.93 & -37.85 & -257.8 \\
\textbf{2004} & 5095 & -5125 & 23.81 & -36.09 & -29.19 \\
\textbf{2005} & 5160 & -3690 & 24.93 & -29.76 & 1469 \\
\textbf{2006} & 5554 & -4210 & 26.2 & -34.22 & 1344 \\
\textbf{2007} & 4938 & -3920 & 23.74 & -35.96 & 1019 \\
\textbf{2008} & 5814 & -4603 & 24.23 & -39.01 & 1212 \\
\textbf{2009} & 5724 & -4746 & 28.06 & -34.39 & 977.8 \\
\textbf{2010} & 4347 & -4191 & 26.84 & -34.92 & 156.5 \\
\textbf{2011} & 1707 & -2171 & 40.65 & -48.24 & -463.5 \\
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1410}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1795}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1795}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1923}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1923}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1154}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\centering
~
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
PositiveSum
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
NegativeSum
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
PositiveMean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
NegativeMean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Sum
\end{minipage} \\
\midrule
\endhead
\textbf{1993} & 3054 & -3389 & 22.13 & -33.56 & -334.9 \\
\textbf{1994} & 6247 & -5727 & 31.24 & -37.93 & 520.4 \\
\textbf{1995} & 4210 & -5814 & 28.45 & -30.93 & -1604 \\
\textbf{1996} & 4206 & -8033 & 26.62 & -41.19 & -3827 \\
\textbf{1997} & 5268 & -6573 & 29.43 & -37.56 & -1304 \\
\textbf{1998} & 5243 & -6363 & 28.34 & -38.56 & -1119 \\
\textbf{1999} & 5920 & -5190 & 28.88 & -33.05 & 730.8 \\
\textbf{2000} & 6699 & -3870 & 29.64 & -29.77 & 2829 \\
\textbf{2001} & 4720 & -5592 & 26.08 & -35.17 & -872.5 \\
\textbf{2002} & 5795 & -6316 & 32.56 & -35.68 & -520.3 \\
\textbf{2003} & 5721 & -6286 & 30.11 & -37.19 & -565.2 \\
\textbf{2004} & 5192 & -5678 & 28.84 & -32.26 & -485.9 \\
\textbf{2005} & 6115 & -4224 & 32.7 & -29.54 & 1891 \\
\textbf{2006} & 6389 & -4608 & 32.43 & -33.63 & 1781 \\
\textbf{2007} & 5666 & -4235 & 29.21 & -34.43 & 1432 \\
\textbf{2008} & 6599 & -4942 & 29.59 & -36.88 & 1656 \\
\textbf{2009} & 6003 & -5238 & 32.28 & -33.58 & 765.2 \\
\textbf{2010} & 4117 & -4603 & 28.01 & -34.1 & -486.4 \\
\textbf{2011} & 1740 & -2226 & 42.43 & -49.46 & -486.1 \\
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1410}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1795}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1795}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1923}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1923}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1154}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\centering
~
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
PositiveSum
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
NegativeSum
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
PositiveMean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
NegativeMean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Sum
\end{minipage} \\
\midrule
\endhead
\textbf{1993} & 556.6 & -1021 & 21.41 & -23.76 & -464.8 \\
\textbf{1994} & 616.9 & -1544 & 17.14 & -22.7 & -926.6 \\
\textbf{1995} & 698 & -899.1 & 17.9 & -21.41 & -201.1 \\
\textbf{1996} & 957.9 & -1481 & 30.9 & -24.28 & -523.2 \\
\textbf{1997} & 1305 & -996.4 & 25.59 & -24.3 & 308.4 \\
\textbf{1998} & 1227 & -761.8 & 24.06 & -18.14 & 465 \\
\textbf{1999} & 754.4 & -1116 & 16.4 & -18.6 & -361.7 \\
\textbf{2000} & 1015 & -993.2 & 22.55 & -21.59 & 21.44 \\
\textbf{2001} & 1047 & -576 & 26.17 & -16.46 & 470.8 \\
\textbf{2002} & 1282 & -1019 & 23.73 & -21.67 & 263 \\
\textbf{2003} & 1123 & -1041 & 26.13 & -21.69 & 82.5 \\
\textbf{2004} & 1395 & -562.8 & 27.9 & -19.41 & 832.3 \\
\textbf{2005} & 904.3 & -1018 & 18.84 & -22.13 & -113.7 \\
\textbf{2006} & 1044 & -929.3 & 21.75 & -23.23 & 114.7 \\
\textbf{2007} & 701.4 & -1082 & 25.05 & -23.03 & -380.8 \\
\textbf{2008} & 916.9 & -1225 & 22.36 & -21.13 & -308.6 \\
\textbf{2009} & 894.8 & -575.7 & 22.37 & -19.85 & 319.1 \\
\textbf{2010} & 790.5 & -469.3 & 23.25 & -19.55 & 321.2 \\
\textbf{2011} & 96.34 & -14.4 & 16.06 & -3.6 & 81.94 \\
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1392}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1772}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1772}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1899}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1899}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1266}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\centering
~
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
PositiveSum
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
NegativeSum
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
PositiveMean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
NegativeMean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Sum
\end{minipage} \\
\midrule
\endhead
\textbf{1993} & 32.03 & -43.15 & 8.008 & -10.79 & -11.12 \\
\textbf{1994} & 38.66 & -59.06 & 6.443 & -9.843 & -20.4 \\
\textbf{1995} & 33.47 & -77.73 & 6.694 & -12.96 & -44.26 \\
\textbf{1996} & 6.869 & -161.9 & 2.29 & -17.99 & -155.1 \\
\textbf{1997} & 33.28 & -61.31 & 8.321 & -7.664 & -28.02 \\
\textbf{1998} & 37.8 & -58.98 & 4.726 & -14.74 & -21.17 \\
\textbf{1999} & 27.94 & -15.43 & 3.992 & -3.086 & 12.51 \\
\textbf{2000} & 101.9 & -10.79 & 9.266 & -10.79 & 91.13 \\
\textbf{2001} & 60.36 & -61.26 & 10.06 & -10.21 & -0.9042 \\
\textbf{2002} & 51.82 & -69.79 & 12.95 & -8.724 & -17.98 \\
\textbf{2003} & 35.53 & -34.82 & 7.106 & -4.974 & 0.7085 \\
\textbf{2004} & 43.12 & -43.88 & 5.39 & -10.97 & -0.7636 \\
\textbf{2005} & 55.88 & -8.827 & 7.983 & -2.207 & 47.06 \\
\textbf{2006} & 50.15 & -25.46 & 7.165 & -6.365 & 24.69 \\
\textbf{2007} & 39.78 & -8.71 & 6.63 & -2.177 & 31.07 \\
\textbf{2008} & 73.43 & -25.38 & 9.179 & -6.345 & 48.05 \\
\textbf{2009} & 66.67 & -38.18 & 9.524 & -7.635 & 28.49 \\
\textbf{2010} & 32.42 & -28.63 & 6.484 & -9.544 & 3.789 \\
\textbf{2011} & 5.498 & -19.1 & 5.498 & -9.55 & -13.6 \\
\bottomrule
\end{longtable}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1392}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1772}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1772}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1899}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1899}}
  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1266}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\centering
~
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
PositiveSum
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
NegativeSum
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
PositiveMean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
NegativeMean
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
Sum
\end{minipage} \\
\midrule
\endhead
\textbf{1996} & 5.182 & -29.29 & 5.182 & -14.64 & -24.11 \\
\textbf{1997} & 37.41 & -8.749 & 18.7 & -4.375 & 28.66 \\
\textbf{1998} & 25.8 & -6.183 & 8.599 & -3.092 & 19.61 \\
\textbf{2000} & 9.461 & -9.806 & 9.461 & -9.806 & -0.3458 \\
\textbf{2001} & 19.95 & -9.823 & 19.95 & -9.823 & 10.13 \\
\textbf{2002} & 42.68 & -10.76 & 21.34 & -5.378 & 31.93 \\
\textbf{2003} & 35.13 & -21.3 & 17.57 & -10.65 & 13.83 \\
\textbf{2005} & 7.114 & -6.776 & 3.557 & -3.388 & 0.3376 \\
\textbf{2006} & 27.81 & -19.11 & 9.269 & -9.554 & 8.698 \\
\textbf{2008} & 5.68 & -15.25 & 2.84 & -5.085 & -9.574 \\
\bottomrule
\end{longtable}

@@
